---
title: "Exercise week 5 - Presentation about me"
author: "Thijs Carriere"
date: "24-11-2021"
output: 
    ioslides_presentation:
      logo: UU_logo.jpg
bibliography: referencesmu5.bib
csl: apa.csl
---

## Outline
1. Still figure
2. Interactive table
3. Interactive figure or movie
4. Multiple columns
5. Equations
6. R code
7. References

## Used packages
```{r message=FALSE, warning=FALSE}
library(tidyverse) # manipulation for frames or tables
library(DiagrammeR) # Figures/diagrams
library(DT) # for tables
```


## Still figure


<center>
This is me

<img src = TCarr.jpg width = 35% />

Thijs Carrière
</center>

## Another still figure

<center>
```{r echo = FALSE}
grViz("
  digraph {
    layout = twopi
    subgraph cluster1 {
    
    node [shape = circle,
          color = mediumvioletred]
    Thijs 
    
    node [shape = diamond,
          color = mediumslateblue]
    Korfbal
    
    node [shape = diamond,
          color = mediumslateblue]
    WIDM
    
    node [shape = diamond,
          color = mediumslateblue]
    boardgames
    
    edge[color = purple]
    Thijs -> WIDM
    
    edge[color = purple]
    Thijs -> Korfbal
    
    edge[color = purple]
    Thijs -> boardgames
    }
  }")
```

</center>

## Interactive table

```{r cache=TRUE, echo = FALSE, out.width="50%"}
setwd("~/Studie/Master/MSBBSS 10 - Markup/Markup_21/Week 5 exercise")
dat1 <- read.csv("winter.csv")

dat1 <- dat1 %>% select(Athlete, Country, Gender, Year, Medal, Sport, Discipline, Event, City)

datatable(dat1, options = list(pageLength = 4, scrollY = TRUE))

# Want to rescale the table, but doesn't work yet ...
```

Since I like to follow sports, here are some random Olympic facts in a table!

## Aftermovie summer camp

<center>
<video width="640" height="480" controls>
  <source src="WIDMmov.mp4" type="video/mp4">
</video>
</center>

## Columns & Equations{.columns-2 .smaller}

$$\begin{aligned}
6\lambda &= 6\alpha + 6\\
\beta + 4 - 2\gamma &= 3\alpha\\
2 + 2\alpha &= 6\\
7\gamma &= 14\lambda + 8\alpha - 9\\
\end{aligned}$$

Find $\beta$
<br><br>
<br>
<br>

Also, picture of my cat on the right to show that I can work in columns

<center>
<img src = kwartje.jpg width = 80%>
</center>


## Code not run
You could obtain $\beta$ with R as a calculator

```{r eval = FALSE}
a <- (6-2)/2
l <- (6*a + 6)/6
g <- (14*l + 8*a - 9)/7
b <- 3*a - 4 + 2*g

print(b)

# spoiler: b should be 16
```

## Some text to include references

Thesis relevant topics with literature:

<br> - Multilevel DIF detection [@dell2021investigating; @gao2019comparison]

<br> - Technology Enhanced Items [@bryant2017developing; @burkhardt2003computer]



## And a literature list